---
title: "R_P_week3"
author: "cs"
date: "27/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r echo=TRUE}
t<-data.frame(c1=1:4,c2=c("a","b","c","d"))
## filter rows based on column 3 == 2
t1<-t[t[,1]==2,]
## below will cause error because it's now defined to filter rows or columns
t1<-t[t[,1]==2]

```

list current local environment variables  
```{r echo=TRUE}
    ls()
```

clear local environment variables  
``` {r echo=FALSE}
    rm(list = ls())
```

if (NA=="NA") will give NA, not a boolean value. 
```{r echo=TRUE}
match("heart attack",c("heart.attack","heart.failure", "pnumonia"))=="NA"
```

for above, should use is.na() instead
```{r echo=TRUE}
is.na(match("heart attack",c("heart.attack","heart.failure", "pnumonia")))
```
if statement, below won't work:
```{r echo=TRUE}
      num<-"worst"
      num<-if(num=="best") 1
      num<-if(num=="worst") 100
```

below works:
```{r echo=TRUE}
      if (num == "best") {
            num<-1
      } else if (num == "worst") {
            num<-nrow(fil)
      }
```

use <<- to define global variable. It's useful if functions at the
same level want to share same variable  

**as.numeric** can't be used to define multiple columns in one dataframe. should use **sapply()** with **as.numeric** to define it.  
